---
title: "Shiny App for calculating annualized returns"
date: "26/09/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What does the application do?

 - The application presents a plot of the DAX and FTSE indices vs time
 
 - The user can select an area of interest in the plot
 
 - The application will calculate the annualized returns for the indices
 in the selected area and report them back
 
 - The application will plot fits through the data using the calculated
 annualized returns
 
 
## Example

```{r, echo=FALSE,message=FALSE}

library(dplyr)
# Load time series data with DAX and FTSE indices
data("EuStockMarkets")
    
# Transform the timeseries to a data frame
stocks <- as.data.frame(EuStockMarkets) %>%
    mutate(time = time(EuStockMarkets))
    
brushed_data <- stocks[1400:1800,]
    
mdlDAX <- lm(log(DAX) ~ time, data = brushed_data)

mdlFTSE <- lm(log(FTSE) ~ time, data = brushed_data)


DAX <- round((exp(mdlDAX[[1]][2])-1)*100,digits=1)


FTSE <- round((exp(mdlFTSE[[1]][2])-1)*100,digits=1)
```

This figure shows a fit for the period 1996.877 - 1998.415 with the following annualized returns: DAX=`r DAX`% and FTSE=`r FTSE`%

```{r}
plot(stocks$time, stocks$DAX, xlab = "Year",
    ylab = "Index", main = "DAX and FTSE indices",
    cex=0.3, col="blue", bty = "n")
points(stocks$time,stocks$FTSE,cex=0.3,col="red")
legend("topleft",pch=1,col=c("blue","red"),legend=c("DAX","FTSE"),bty="n")
lines(brushed_data$time,exp(predict(mdlDAX)),col="blue",lwd=4)
lines(brushed_data$time,exp(predict(mdlFTSE)),col="red",lwd=4)

```

## Some technical stuff

To determine the annualized returns of the indices, the indices are modeled
in the following way:  
 
`index = a * ( 1 + R )^t`
 
where `a` is some constant, `R` the annualized return as a fraction and `t` is time in years.

The annualized returns `R` were estimated by fitting `log(index)` vs `t` using a linear model.

The slope of the fit equals `log(1+R)` from which `R` can be determined.

## Thank you for your attention

The application can be found by following this link: [https://tsuyoshi-matsuura.shinyapps.io/InteractiveGraphics](https://tsuyoshi-matsuura.shinyapps.io/InteractiveGraphics)


I hope you enjoy playing with the application!!!!!
